---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(knitr)
```

# Reprex & Observatories Brand Identiy

<!-- badges: start -->
[![dataobservatory](https://img.shields.io/badge/ecosystem-dataobservatory.eu-3EA135.svg)](https://dataobservatory.eu/)

<!-- badges: end -->


```{r templateexample, message=FALSE, echo=FALSE}
library(dplyr)
library(ggplot2)
library(reprextemplates)

data.frame (
  Color = names(reprex_palette()), 
  HEX = as.character(reprex_palette()),
  values = rep(1,12)
 ) %>%
  ggplot( aes (x = Color, 
               y = values, 
               fill = Color)) +
  geom_col() +
  scale_fill_manual( values = reprex_palette()) +
  theme_minimal() +
  labs ( y = NULL, x = NULL, title = "Reprex & Observatory Color Palette") +
  theme(axis.text.x=element_blank(),
      axis.ticks.x=element_blank(),
      axis.text.y=element_blank(),
      axis.ticks.y=element_blank(), 
      panel.grid.major = element_blank())

```

```{r, results='asis'}
kable(
  data.frame (
  Color = names(reprex_palette()), 
  HEX = as.character(reprex_palette())
 )
)
```

## Fonts

In headings please use `Roboto`.  In text, you can use `Roboto Light` or `Roboto Condensed`, or similar fonts.

## Installation

If you want to use in the palette in R, for example, in ggplot2, you need to install the development version of reprextemplates from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dataobservatory-eu/reprextemplates")
```

```{r reprextemplate, echo=TRUE}
library(reprextemplates)
reprex_palette()
```

## Code of Conduct
  
Please note that the reprextemplates project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
# brand_identity_media